%% Basic document used to render the PDF.

\documentclass[10pt]{article}

\usepackage{mathtools}
\usepackage{hyperref}

\begin{document}

%DATE:2020-10-01
%TIME:3:55pm

\section*{Recap of meeting on 30/9 with \href{mailto:k.mengersen@qut.edu.au}{\textbf{Kerrie Mengersen}}}

\subsection*{DSS Papers}
On difference in Linear Regression (LR) versus random forest (RF) width in rank:
\begin{enumerate}
    \item Which are wider for Random Forests, and do they sit at extremes?
    \item Is the difference very small (on average)?
    \item A ratio of widths may be a good method to tease it out.
\end{enumerate}

Paragraph to address \href{mailto:p.wu@qut.edu.au}{\textbf{Paul Wu}}'s comments: Either say that it explicitly doesn't address the issues which \href{mailto:p.wu@qut.edu.au}{\textbf{PW}} raises, or that the method could be embedded or extended to address the issues. Check that \href{mailto:p.wu@qut.edu.au}{\textbf{PW}} is OK with it, then submit.

Acknowledgements: need to acknowledge the funding by ARC Laureate fellowship and also ``the agency'' (preserving anonymity) which contributed financial support to the research.
\subsection*{Mixture Testing}
\href{mailto:k.mengersen@qut.edu.au}{\textbf{KM}} is looking for a clinical trial with a standard template and standard decision rules (for evidence). A trial with a Bayes Factor method may be useful, or look for Don Berry's work (Bayesian clinical trial advocate).


Time: 3:55pm
  
\end{document}